Gammapy: A Python package for gamma-ray astronomy

### 2023-01-23 src/ms-review.tex
Add big picture figure
Add Fig 1 caption

\abstract{

	{Context} Traditionally, the \gammaray universe has been probed
	 by small collaborations of scientists employing proprietary data and analysis software.
	 However, the next generation of \gammaray instruments,
	 such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
	 Alongside the data, the observatories will make available to the astronomical community
	 software tools for their analysis. This necessity prompted the development, in the last decade,
	 of open high-level astronomy software customised for high energy astrophysics.

	{Aims} In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
	and illustrate the functionalities of the first long-term release of the software, version 1.0.
	Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
	modelling data from different gamma-ray instruments. \gammapy complies with several well-established
	data conventions in high-energy astrophysics, providing serialised data products that are interoperable
	with other software.

	{Methods} Starting from event list and instrument response functions",
	\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
	To facilitate the handling of the hadronic background, several techniques for background estimation
	 are implemented in the package.
	 After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
	 using Poisson maximum likelihood fitting
	 and assuming a variety of spectral, temporal, and spatial models.
	  Estimation of flux points, likelihood profiles and light curves are also implemented.

	{Results} After describing the structure of the package, we demonstrate the capabilities of \gammapy
	performing several traditional analyses in gamma-ray astronomy with publicly available data:
	spectral and spectro-morphological analyses, estimation of the light curve of a source.
	The flexibility and power of the software are displayed in a final multi-instrument example,
	where data sets from different instruments, at different stages of data reduction,
	are simultaneously fitted with a flux model produced by another astrophysical software.
}

@@

>>>>

\abstract
	{
		Traditionally, the \gammaray universe has been probed
		by small collaborations of scientists employing proprietary data and analysis software.
		However, the next generation of \gammaray instruments,
		such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
		Alongside the data, the observatories will make available to the astronomical community
		software tools for their analysis. This necessity prompted the development, in the last decade,
		of open high-level astronomy software customised for high energy astrophysics.
	}
	{
		In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
		and illustrate the functionalities of the first long-term release of the software, version 1.0.
		Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
		modelling data from different gamma-ray instruments. \gammapy complies with several well-established
		data conventions in high-energy astrophysics, providing serialised data products that are interoperable
		with other software.
	}
	{
		Starting from event list and instrument response functions",
		\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
		To facilitate the handling of the hadronic background, several techniques for background estimation
		are implemented in the package.
		After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
		using Poisson maximum likelihood fitting
		and assuming a variety of spectral, temporal, and spatial models.
		Estimation of flux points, likelihood profiles and light curves are also implemented.
	}
	{
		After describing the structure of the package, we demonstrate the capabilities of \gammapy
		performing several traditional analyses in gamma-ray astronomy with publicly available data:
		spectral and spectro-morphological analyses, estimation of the light curve of a source.
		The flexibility and power of the software are displayed in a final multi-instrument example,
		where data sets from different instruments, at different stages of data reduction,
		are simultaneously fitted with a flux model produced by another astrophysical software.
	}{}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
	\caption{
		Core idea and relation of \gammapy to different \gammaray instruments
		and the gamma astro data formats (GADF). The top left shows the
		group of current and future pointing instruments based on the 
		imaging atmospheric Cherenkov technique (IACT). This includes
		instruments such as the  Cherenkov Telescope Array (CTA),
		the High Energy Stereoscopic System (H.E.S.S.), the
		Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC),
		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
		The lower left shows the group of allsky instruments such as the
		Fermi Large Area Telescope (Fermi-LAT) amd the High Altitude 
		Water Cherencov Observatory (HAWC). The calibrated data of all those
		instruments can be converted and stored into the common GADF data format.
		\gammapy can read data stored in the GADF format.
		The \gammapy package is not a part of any instrument, but instead
		provides a common interface to the data and analysis of all
		these \gammaray instruments. This way users can also easily combine data from
		different instruments and perform a joint analysis. 
	}
	\label{fig:big_picture}

\end{figure*}
